\begin{rubric}{Miscellaneous Experience}
\subrubric{Awards}
\entry*[12/2017] Jiangxi Provincial College Students' Science and Technology Innovation and Vocational Skills Competition, Electronic Comprehensive Design Competition, First Prize of Undergraduate Group.
%
\entry*[08/2017] Jiangxi Provincial College Students' Science and Technology Innovation and Vocational Skills Competition, Electronic Thematic Design Competition, Second Prize of Undergraduate Group.

\subrubric{Certifications}
\entry*[04/2022] \textbf{International English Language Testing System (IELTS): Overall band score 7.0 (Listening 7.5, Reading 7.5, Writing 6.5, Speaking 6.0)}

\entry*[07/2017] \textbf{Fitness Coach Licentiate (FCL): Awarded by The Ministry of Human Resource and Social Security, The People's Republic of China.}

\subrubric{Volunteer Works}
\entry*[03/2022] Volunteer in Northwestern Polytechnical University's COVID-19 epidemic prevention and control volunteer service.

\entry*[07/2019] Participate in the "Guarding the Qinling Mountains, College Students in Action" public welfare and environmental protection activity.

\subrubric{Involved Projects}
% \entry*[03/2023-Present] Research on universal adversarial attack technology based on background perturbation generation.

\entry*[09/2022-02/2023] Research on the robustness of remote sensing image classification and object detection model based on deep learning.

\entry*[12/2021-08/2022] Research on cross-domain lossless evolution of adversarial perturbations for physical attack. \textbf{Relevant research achievements received an interview invitation from the British authoritative magazine New Scientist}.

\subrubric{Internship}
\entry*[07/2021-09/2021] Internship at AVIC Xi'an Flight Automatic Control Research Institute.
\entry*[07/2020-09/2020] Internship at Xi'an Institute of Modern Control Technology.

\end{rubric}