\makerubrichead{Research Publications}

\vspace{4pt}
{\large\bfseries\sffamily\hspace{3pt}Journal Articles}
\par
\vspace{0.3cm}

\noindent\textbf{[1]} \textbf{Jiawei Lian}, Jianhong Pan, Lefan Wang, Yi Wang, Shaohui Mei, Lap-Pui Chau. ``PADetBench: Towards Benchmarking Physical Attacks against Object Detection.'' \textit{Knowledge-Based Systems}, 2025.

\vspace{0.3cm}
\noindent\textbf{[2]} Shaohui Mei, \textbf{Jiawei Lian}, Xiaofei Wang, Yuru Su, Mingyang Ma, Lap-Pui Chau. ``A Comprehensive Study on the Robustness of Image Classification and Object Detection in Remote Sensing: Surveying and Benchmarking.'' \textit{Journal of Remote Sensing}, 2024. (\textit{The first author is the Ph.D. advisor})

\vspace{0.3cm}
\noindent\textbf{[3]} \textbf{Jiawei Lian}, Xiaofei Wang, Yuru Su, Mingyang Ma, Shaohui Mei. ``CBA: Contextual Background Attack against Optical Aerial Detection in the Physical World.'' \textit{IEEE Transactions on Geoscience and Remote Sensing}, vol. 61, pp. 1--16, 2023.

\vspace{0.3cm}
\noindent\textbf{[4]} \textbf{Jiawei Lian}, Shaohui Mei, Shun Zhang, Mingyang Ma. ``Benchmarking Adversarial Patch against Aerial Detection.'' \textit{IEEE Transactions on Geoscience and Remote Sensing}, vol. 60, pp. 1--16, 2022.

\vspace{0.3cm}
\noindent\textbf{[5]} \textbf{Jiawei Lian}, Junhong He, Yun Niu, Tianze Wang. ``Fast and Accurate Detection of Surface Defect Based on Improved YOLOv4.'' \textit{Assembly Automation}, vol. 42, no. 1, pp. 134--146, 2021.

\vspace{0.3cm}
\noindent\textbf{[6]} \textbf{Jiawei Lian}, Junhong He, Yun Niu, Tianze Wang. ``Rapid Detection of Surface Defects Based on Multi-scale Compression CNN.'' \textit{Computer Integrated Manufacturing System}, vol. 28, no. 11, pp. 3624, 2021.

\vspace{0.5cm}
{\large\bfseries\sffamily\hspace{3pt}Conference Papers}
\par
\vspace{0.3cm}

\noindent\textbf{[1]} \textbf{Jiawei Lian}, Jianhong Pan, Lefan Wang, Yi Wang, Shaohui Mei, Lap-Pui Chau. ``Semantic Representation Attack against Aligned Large Language Models.'' \textit{Advances in Neural Information Processing Systems (NeurIPS)}, 2025.

\vspace{0.3cm}
\noindent\textbf{[2]} \textbf{Jiawei Lian}, Xiaofei Wang, Yuru Su, Mingyang Ma, Shaohui Mei. ``Contextual Adversarial Attack against Aerial Detection in the Physical World.'' \textit{IEEE International Geoscience and Remote Sensing Symposium (IGARSS)}, pp. 6632--6635, 2023.

\vspace{0.5cm}
{\large\bfseries\sffamily\hspace{3pt}Preprints}
\par
\vspace{0.3cm}

\noindent\textbf{[1]} \textbf{Jiawei Lian}, Jianhong Pan, Lefan Wang, Yi Wang, Xiaofei Wang, Yingjie Lu, Shaohui Mei, Lap-Pui Chau. ``Revealing the Intrinsic Ethical Vulnerability of Aligned Large Language Models.'' \textit{arXiv preprint arXiv:2504.05050}, 2025. (\textbf{Under second round review, Nature Communications})

\vspace{0.3cm}
\noindent\textbf{[2]} \textbf{Jiawei Lian}, Shaohui Mei, Xiaofei Wang, Yi Wang, Lefan Wang, Yingjie Lu, Mingyang Ma, Lap-Pui Chau. ``Attack Anything: Blind DNNs via Universal Background Adversarial Attack.'' \textit{arXiv preprint arXiv:2409.00029}, 2024. (\textbf{Under review, IEEE Transactions on Dependable and Secure Computing})

